Modeling Bandwagoning and Hype in the MLB

### 2020-08-31 Paper_Outline.Rmd
more model details

## Measuring hype and bandwagoning

>>>>

(motivation for hierarchical model)

(for sections below, provide discussion of model in words, and summary of model results)

### Level 1: Overall predicted mean

$$\{\text{Mean google hits overall} \} \sim \{\text{Mean google hits for all teams} \} + \alpha \, \text{\{TV Market Size\}} + \epsilon_{i}$$

### Level 2: Annual predicted mean

$$\{\text{Mean google hits this year} \} \sim 
\{\text{Mean google hits overall} \} + 
\gamma_0 \{\text{MLB google hits this year}\} + 
\gamma_{1} \{\text{Mean google hits last year}\} +
\gamma_{2} \{\text{Playoffs last year}\} +
\gamma_{3} \{\text{Win percent last year}\} +
\gamma_{4} \{\text{Preseason odds}\} +
\gamma_{5} \{\text{Preseason payroll}\} +
\epsilon_{ij}
\; $$

### Level 3: Predicted Google hits by month

## Results

(A few plots and discussion of how well the model fits)

## Measuring bandwagoning
